Code to reproduce results in _Semi-parametric generalized linear model for

### 2022-03-19 ManuscriptCode/Manuscript.Rmd
Tweak manuscript plots

---
title: Code to reproduce results in _Semi-parametric generalized linear model for
  binomial data with varying cluster sizes_
author: "Aniko Szabo"
output:
  html_document:
    df_print: paged
---

@@

ggplot(fits, aes(x=NResp, y=Prob, colour=Model)) +
  facet_wrap(~Trt) +
  geom_point() +
  geom_line() +
  scale_x_continuous("# of affected animals", breaks=seq(0,10,by=2)) +
  ylab("Probability") +
  theme_bw()

@@

```{r SimOne}
beta_correct <- c(0, 0.5, 1)
sim_covariates <- function(n, maxClusterSize = 10, aveClusterSize = 7, beta=beta_correct){
  x1 <- rbinom(n, size=1, prob=0.5)
  x2 <- rnorm(n)
  lp <- cbind(1, x1, x2) %*% beta
  mns <- 1/(1+exp(-lp))

@@

```{r ActualSim1, warning=FALSE}
R <- 500
cs_predict <- 5
p_predict <- 1/(1+exp(-c(beta_correct %*% c(0,0,0))))

# Scenario 1: binomial PDF
sim1 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbinom(n, size=cs, prob=p));
             run_analysis(simd, cs_predict = cs_predict, Binom = TRUE)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r ActualSim2, warning=FALSE}
# Scenario 2: beta-binomial PDF
sim2 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbetabinom(n, size=cs, prob=p, rho=0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE) %>%
   bind_rows(.id="ID")

@@

```{r ActualSim3, warning=FALSE}
# Scenario 3: SPGLM with q-power backbone
sim3 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
              add_response_spglm(q0 = qpower.pdf(n=10, p=0.4, rho = 0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r ActualSim4, warning=FALSE}
# Scenario 4: q-power 
sim4 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rqpower(n, size=cs, prob=p, rho=0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

comb_beta <- left_join(comb %>% filter(Type == "Beta"), correct_beta, by="Term")

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se / mc.se[Model=="GEE"],
         se.rel.bias = mc.se/se) %>%
  ungroup() %>%
  arrange(Generator, Model, Term)
kable(scomb, digits=3)
```

```{r ComparePlot}
cols <- RColorBrewer::brewer.pal(3, "Set2")
names(cols) <- levels(comb$Model)
ggplot(comb_beta, aes(x=Term, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(aes(yintercept=0)) +
  geom_boxplot(position=position_dodge(width=0.4), width=0.3, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Bias = Estimate - correct value") +
  scale_fill_manual(breaks=names(cols), values=cols)

@@

```{r PDFplot}
ggplot(comb_pdf, aes(x=NResp, y=Est, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_line(aes(y=Correct), colour="black", size=1) +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.6), width=0.5, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Probability") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols)

ggplot(comb_pdf, aes(x=NResp, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(yintercept = 0, colour="black", size=1) +
  stat_summary(aes(color=Model), fun=mean, geom="line") +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.6), width=0.5, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Bias of probability") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols)

>>>>

---
title: Code to reproduce results in _Semi-parametric generalized linear model for
  binomial data with varying cluster sizes_
author: "Aniko Szabo"
output:
  pdf_document: 
    keep_tex: true
  html_document:
    df_print: paged
---

@@

linecols <- colorspace::darken(RColorBrewer::brewer.pal(3, "Set3"), 0.2)
names(linecols) <- unique(fits$Model)

ggplot(fits, aes(x=NResp, y=Prob, colour=Model, shape=Model, linetype=Model)) +
  facet_wrap(~Trt) +
  geom_point() +
  geom_line() +
  scale_x_continuous("# of affected animals", breaks=seq(0,10,by=2)) +
  scale_colour_manual(values=linecols) +
  ylab("Probability") +
  theme_bw()

@@

```{r SimParams}
R <- 500
beta_correct <- c(0, 0.5, 1)
cs_predict <- 5
p_predict <- 1/(1+exp(-c(beta_correct %*% c(0,0,0))))
```

```{r SimOne}
sim_covariates <- function(n, maxClusterSize = 10, aveClusterSize = 7, beta=beta_correct){
  x1 <- rbinom(n, size=1, prob=0.5)
  x2 <- rnorm(n)
  lp <- cbind(1, x1, x2) %*% beta
  mns <- 1/(1+exp(-lp))

@@

```{r ActualSim1, warning=FALSE}
set.seed(20211223)
# Scenario 1: binomial PDF
sim1 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbinom(n, size=cs, prob=p));
             run_analysis(simd, cs_predict = cs_predict, Binom = TRUE)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r ActualSim2, warning=FALSE}
set.seed(20211223)
# Scenario 2: beta-binomial PDF
sim2 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbetabinom(n, size=cs, prob=p, rho=0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE) %>%
   bind_rows(.id="ID")

@@

```{r ActualSim3, warning=FALSE}
set.seed(20211223)
# Scenario 3: SPGLM with q-power backbone
sim3 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
              add_response_spglm(q0 = qpower.pdf(n=10, p=0.4, rho = 0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r ActualSim4, warning=FALSE}
set.seed(20211223)
# Scenario 4: q-power 
sim4 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rqpower(n, size=cs, prob=p, rho=0.3));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

comb_beta <- left_join(comb %>% filter(Type == "Beta"), correct_beta, by="Term") %>%
  mutate(Coefficient = recode(Term, "(Intercept)" = "beta[0]", 
                              "X1"="beta[1]", 
                              X2="beta[2]"),
         Term = recode(Term,  "(Intercept)" = "$\\beta_0$", 
                       "X1"="$\\beta_1$", 
                       X2="$\\beta_2$"))

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se / mc.se[Model=="GEE"]) %>%
  ungroup() %>%
  arrange(Generator, Model, Term)
kable(scomb, digits=3)
```

```{r ComparePlot}
cols <- RColorBrewer::brewer.pal(3, "Set3")
names(cols) <- levels(comb$Model)
ggplot(comb_beta, aes(x=Coefficient, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(aes(yintercept=0)) +
  geom_boxplot(position=position_dodge(width=0.8), width=0.7, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_x_discrete(labels = scales::label_parse()) +
  scale_y_continuous("Bias of parameter estimate") +
  scale_fill_manual(breaks=names(cols), values=cols) +
  theme(legend.position = "top")

@@

```{r PDFplot}
ggplot(comb_pdf, aes(x=NResp, y=Est, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_line(aes(y=Correct), colour="black", size=1) +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.6), width=0.5, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Probability") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols)  +
  theme(legend.position = "top")

ggplot(comb_pdf, aes(x=NResp, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(yintercept = 0, colour="black") +
 # stat_summary(aes(color=Model), fun=mean, geom="line") +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.8), width=0.7, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Bias of event probability estimate") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols) +
  theme(legend.position = "top")
